Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-11-01 paper/paper.tex
finish paragraph on musical training
write on the influence of pitch on timbre perception

We did not collect personal information on the age, sex, nor musical background of participants.
This is because the goal of our perceptual study is to build a consensus of similarity judgments, rather than to compare demographic subgroups.
We note that the relatively small size of our cohort ($K=31$) lacks the statistical power to carry out such a comparison.
In particular, we leave the important question of the effect of musical training on the  as future work.

@@

>>>>

We did not collect personal information on the age, sex, nor musical background of participants.
This is because the goal of our perceptual study is to build a consensus of similarity judgments, rather than to compare demographic subgroups.
We note that the relatively small size of our cohort ($K=31$) lacks the statistical power to carry out such a comparison.
In particular, we leave the important question of the effect of musical training on the perception of auditory similarities between playing techniques as future work.
% TODO revise the paragraph above

@@

Underlying our label propagation procedure is the assumption that the perception of timbre is fully invariant to frequency transposition as well as changes in dynamics.
This assumption coincides with the commonplace definition of timbre as an autonomous parameter of musical sound.
Previous studies on real-world musical sounds have confirmed that listeners are able to ignore salient pitch differences while rating timbre similarity \cite{handel2001musicperception,marozeau2003dependency}, insofar as these differences do not exceed one octave.
Since then, another study has shown that trained musicians can identify the similarity within pairs of notes from two instruments (horn and bassoon) spanning a range of $2.5$ octave with an accuracy of $80\%$ \cite{steele2006musicperception}.
In comparison, nonmusicians has great difficulty identifying whether two notes were produced by the same instrument or not when the notes were separated by one octave.
Thus, the influence of pitch on timbre perception appears to depend upon musical training.
With this important caveat in mind, we leave as future work the question of disentangling the effect of pitch and musical training in the modeling of auditory similarities between instrumental playing techniques.
